Software Architectures for Integrating Workflow Engines in Science Gateways

### 2016-05-13 paper.tex
done up to before 3.2

\emph{Specific features} include:
\begin{itemize}[leftmargin=0cm,itemindent=0.35cm,itemsep=0cm]
\item Meta-workflow (\texttt{O$_1$}): ability to describe
  meta-workflows from existing workflows. Meta-workflows offer an
  additional level of flexibility to build workflows from reusable
  components. \texttt{O$_1$}=0 when the feature is available,
  \texttt{O$_1$}=1 otherwise.
\item Fine-grained debugging (\texttt{O$_2$}): availability of
  fine-grained debugging information about workflow tasks (white-box
  workflow).  Fine-grained information about workflow tasks is
  required to properly troubleshoot workflow executions.
  \texttt{O$_2$}=0 when such information is easy to access,
  \texttt{O$_2$}=1 otherwise.
\end{itemize}
\texttt{O$_1$} and \texttt{O$_2$} are summed to obtain a total number of missing specific
features in the architecture.

>>>>

\emph{Specific features} include:
\begin{itemize}[leftmargin=0cm,itemindent=0.35cm,itemsep=0cm]
\item Meta-workflow (\texttt{O$_1$}): measures the ability to describe
  meta-workflows from existing workflows. Meta-workflows offer an
  additional level of flexibility to build workflows from reusable
  components. \texttt{O$_1$}=0 means that the feature is available, and
  \texttt{O$_1$}=1 otherwise.
  \note{si}{why here we do not have the "possible to implement" situation?}

\item Fine-grained debugging (\texttt{O$_2$}): availability of
  fine-grained debugging information about workflow tasks (white-box
  workflow).  Fine-grained information about workflow tasks is
  required to properly troubleshoot workflow executions.
  \texttt{O$_2$}=0 means that such information is easy to access, and
  \texttt{O$_2$}=1 otherwise.
\end{itemize}
\texttt{O$_1$} and \texttt{O$_2$} are summed to obtain a total number of missing specific
features in the architecture.
